Title

### 2023-08-14 manu-draft.qmd
rework threshold temp plots for diff ranges and fix polygon order

@@

-   Salinity: 25 (lower, @lewis1985); 30, lowest at 5 (lower, @lirman2003), 33-38 (range, @phillips1960); 24-35 (range, @zieman1975 citing @phillips1960)

@@

-   Salinity: 20 (lower, @lewis1985), 25 (lower, @lirman),

>>>>

Focus on two time periods: full record and recent decline

Focus on two physical parameters: temperature and salinity

Temp background for TB: NOAA coastwatch trends

@@

-   Salinity: 25 (lower, @lewis1985); 30, lowest at 5 (lower, @lirman2003), 33-38 (range, @phillips1960); 24-35 (range, @zieman1975 citing @phillips1960); avg 28

@@

-   Salinity: 20 (lower, @lewis1985), 25 (lower, @lirman2003); avg 22.5
